My title

### 2024-09-23 paper/paper.qmd
add some information of the graph

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

@@

# Load ggplot2 for plotting
ggplot(total_population_data, aes(x = Date, y = Homeless_Count)) +
  geom_line(color = "blue", linewidth = 1.5) +  # Adjust line color and width
  labs(title = "Total Homeless Population Over Time",
       x = "Date",
       y = "Homeless Population Count") +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +  # Show year on x-axis with 1-year intervals
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}

@@

# Create a pie chart with percentage labels
ggplot(total_data_long, aes(x = "", y = Count, fill = Age_Group)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
  geom_text(aes(label = paste0(Percent, "%")), 
            position = position_stack(vjust = 0.5), size = 4) +
  labs(title = "Age Group Distribution of Total Homeless Population") +
  theme_void() +
  theme(legend.position = "right") +
  scale_fill_brewer(palette = "Set3")  # Use a color palette for clarity

```{r}

# Read the cleaned data
cleaned_shelter_data <- read.csv("/Users/liz/Downloads/starter_folder-main/data/analysis_data/shelter_analysis_data.csv")

# Ensure the date column is in the correct format
cleaned_shelter_data$date <- as.Date(paste0("01-", cleaned_shelter_data$Date), format="%d-%b-%y")
cleaned_shelter_data$year <- format(cleaned_shelter_data$date, "%Y")  # Extract year as a string

# Summarize data by year for different age groups
age_data <- cleaned_shelter_data %>%
  group_by(year) %>%
  summarise(Age_Under_16 = sum(Age_Under_16, na.rm = TRUE),
            Age_16_24 = sum(Age_16_24, na.rm = TRUE),
            Age_25_34 = sum(Age_25_34, na.rm = TRUE),
            Age_35_44 = sum(Age_35_44, na.rm = TRUE),
            Age_45_54 = sum(Age_45_54, na.rm = TRUE),
            Age_55_64 = sum(Age_55_64, na.rm = TRUE),
            Age_65_Over = sum(Age_65_Over, na.rm = TRUE))

# Reshape data for plotting
age_data_long <- pivot_longer(age_data, 
                              cols = starts_with("Age"), 
                              names_to = "Age_Group", 
                              values_to = "Count")

# Plot 100% stacked bar chart
ggplot(age_data_long, aes(x = year, y = Count, fill = Age_Group)) +
  geom_bar(stat = "identity", position = "fill") +  # Use 'fill' to normalize to 100%
  scale_y_continuous(labels = percent) +  # Display percentages on y-axis
  labs(title = "Age Group Proportion Over Time", 
       x = "Year", y = "Proportion", fill = "Age Group") +
  theme_minimal() +
  scale_fill_brewer(palette = "Set3")  # Use color palette for clarity

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

# Read the cleaned data
cleaned_shelter_data <- read.csv("/Users/liz/Downloads/starter_folder-main/data/analysis_data/shelter_analysis_data.csv")

@@

# Plot area chart with percentages in the legend
ggplot(gender_data_long, aes(x = year, y = Count, fill = Gender)) +
  geom_area(position = "stack") +
  labs(title = "Homeless Population by Gender Over Time (Area Chart)", 
       x = "Year", y = "Homeless Population Count", fill = "Gender") +
  scale_fill_manual(values = c("Male" = "blue", "Female" = "pink", "Non_Binary" = "purple"),
                    labels = gender_percentages) +  # Add percentages to the legend
  theme_minimal()

@@

Talk way more about it. 
```{r}

@@

# Plot the stacked bar chart with Chronic at the top
ggplot(combined_data, aes(x = year, y = homeless_count, fill = group)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(title = "Chronic vs Non-Chronic Homeless Population by Year", 
       x = "Year", y = "Homeless Population Count", fill = "Group") +
  theme_minimal() +
  scale_fill_manual(values = c("Chronic" = "blue", "Non-Chronic" = "orange"))  # Adjust colors if needed

@@

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Jianing Li
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

# Data {#sec-data}
## Overview {#sec-data-overview}
Some of our data is of penguins (@fig-bills), from @palmerpenguins.

## Results {#sec-data-results}

```{r}
#| echo: false
#| warning: false
#| label: fig-total-population
#| fig-cap: "Trend of Homeless Population in Toronto from 2018 to 2024"

@@

# Load ggplot2 for plotting
ggplot(total_population_data, aes(x = Date, y = Homeless_Count)) +
  geom_line(color = "blue", linewidth = 1.5) +  # Adjust line color and width
  labs(x = "Date",
       y = "Homeless Population Count") +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +  
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

@fig-total-population illustrates the fluctuation in Toronto's homeless population from 2018 to 2024. The chart shows cyclical rises and falls, with more pronounced declines around 2020 and 2021, followed by a steady recovery. The population reaches its highest point in 2024. Throughout this period, the homeless population varies between approximately 7,500 and 11,000 individuals.

```{r}
#| echo: false
#| warning: false
#| label: fig-age-distribution
#| fig-cap: "Age Group Distribution of Homeless Population in Toronto (2018-2024)"

@@

# Create a pie chart with percentage labels
ggplot(total_data_long, aes(x = "", y = Count, fill = Age_Group)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y") +
  geom_text(aes(label = paste0(Percent, "%")), 
            position = position_stack(vjust = 0.5), size = 4) +
  theme_void() +
  theme(legend.position = "right") +
  scale_fill_brewer(palette = "Set3")  # Use a color palette for clarity

```
@fig-age-distribution shows the percentage of Toronto's homeless population in each age group as a proportion of the total homeless population from 2018 to 2024. The largest age group is 35-44 years old, accounting for about 21\% of the total population, followed by the 25-34 age group (approximately 18\%), the 45-54 age group (approximately 17\%), and the 55-64 age group (approximately 14\%). The under 16 and 16-24 age groups each account for 12\%. The smallest age group is 65 years and above, making up about 7\% of the total population.

```{r}
#| echo: false
#| warning: false
#| label: fig-gender-distribution
#| fig-cap: "Homeless Population by Gender in Toronto (2018-2024)"
#| 
# Read the cleaned data
cleaned_shelter_data <- read.csv("/Users/liz/Downloads/starter_folder-main/data/analysis_data/shelter_analysis_data.csv")

@@

# Plot area chart with percentages in the legend
ggplot(gender_data_long, aes(x = year, y = Count, fill = Gender)) +
  geom_area(position = "stack") +
  labs(x = "Year", y = "Homeless Population Count", fill = "Gender") +
  scale_fill_manual(values = c("Male" = "blue", "Female" = "pink", "Non_Binary" = "purple"),
                    labels = gender_percentages) +  # Add percentages to the legend
  theme_minimal()

@@

@fig-gender-distribution presents the gender distribution of Toronto's homeless population from 2018 to 2024. During this period, males have consistently made up the largest proportion, accounting for approximately 61.8% of the total homeless population. Females make up about 36.8%, while non-binary individuals make up about 1.4%. Over time, the total homeless population of each gender has shown similar trends, meaning that the proportion of each gender has remained almost constant.

```{r}
#| echo: false
#| warning: false
#| label: fig-chronic-population
#| fig-cap: "Comparison of Chronic vs Non-Chronic Homeless Population in Toronto (2019-2024)"

@@

# Plot the stacked bar chart with Chronic at the top
ggplot(combined_data, aes(x = year, y = homeless_count, fill = group)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(x = "Year", y = "Homeless Population Count", fill = "Group") +
  theme_minimal() +
  scale_fill_manual(values = c("Chronic" = "blue", "Non-Chronic" = "orange"))  # Adjust colors if needed

@@

@@

@@
